A Cross-Benchmark Comparison of 87 Learning to Rank Methods

### 2014-05-27 cikm_paper/paper.tex
gecorrigeerde waarden
paper mooi

\subsection{Literature Selection}
Table \ref{tab:ltr_methods_used} in the appendix gives an overview of the learning to rank methods for which evaluation results were found through the described procedure. Occurrences of L2, L3 and L4 in Table \ref{tab:ltr_methods_used} imply that these algorithms are evaluated as official LETOR 2.0, 3.0 and 4.0 baselines respectively.\\

@@

\subsection{Cross-Metric}
\begin{figure}
\centering
\includegraphics[scale=0.21]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_all}
\end{figure}
Figure \ref{fig:normalized_winning_number_all} shows the NWN as function of IWN for the methods described in Table \ref{tab:ltr_methods_used}. The cross-metric comparison is based on the NDCG@$\{3,5,10\}$ and MAP comparisons combined, which justifies analyzing the comparison more thoroughly. Figure \ref{fig:normalized_winning_number_all} labels the algorithms with no other algorithm having a higher value on both the horizontal axis and vertical axis, but also labels the algorithms with exactly one algorithm having a higher value on both axes with smaller font size. In addition, Linear Regression and the ranking method of simply sorting on the best single feature are labelled as baselines.\\

@@

\label{app:ltr_methods_used}
\label{app:raw_data}

@@

AdaRank-MAP & 0.3486 & 12 && 0.3884 & 12 && 0.3648 & 13 && 0.3206 & 12 && 332 & 937 & 0.3543 \\
AdaRank-NDCG & 0.3073 & 12 && 0.3259 & 12 && 0.3158 & 16 && 0.2863 & 12 && 293 & 951 & 0.3081 \\

@@

ApproxNDCG & 0.7949 & 1 && 0.7500 & 1 && 0.8611 & 1 && - & - && 92 & 115 & 0.8000 \\
BagBoo & 0.8478 & 2 && 0.8400 & 1 && - & - && 0.6545 & 2 && 96 & 126 & 0.7619 \\

@@

BL-MART & 0.9524 & 2 && 0.7200 & 1 && - & - && 0.8036 & 3 && 83 & 102 & 0.8137 \\
BoltzRank-Pair & 0.8333 & 4 && 0.8350 & 4 && - & - && 0.5804 & 5 && 254 & 348 & 0.7299 \\
BoltzRank-Single & 0.7549 & 4 && 0.7184 & 4 && - & - && 0.4336 & 5 && 213 & 348 & 0.6121 \\

@@

CoList & 1.0000 & 1 && - & - && 0.1667 & 1 && - & - && 2 & 7 & 0.2857 \\

@@

DCMP & 0.5459 & 9 && 0.5079 & 9 && 0.5888 & 9 && - & - && 320 & 584 & 0.5479 \\

@@

EnergyNDCG & 0.3636 & 2 && 0.3778 & 2 && 0.4146 & 2 && - & - && 50 & 130 & 0.3846 \\
FBPCRank & 0.4146 & 3 && 0.5529 & 3 && - & - && - & - && 81 & 167 & 0.4850 \\
FenchelRank & 0.7742 & 5 && 0.7500 & 5 && 0.7623 & 5 && 0.6418 & 5 && 368 & 504 & 0.7302 \\
FocusedBoost & 0.3750 & 2 && 0.4545 & 2 && 0.6863 & 2 && - & - && 73 & 143 & 0.5105 \\

@@

FocusedSVM & 0.2500 & 2 && 0.2727 & 2 && 0.6078 & 2 && - & - && 55 & 143 & 0.3846 \\

@@

FRank & 0.3085 & 11 && 0.2849 & 10 && 0.3029 & 11 && 0.2623 & 11 && 242 & 839 & 0.2884 \\
FSMRank & 0.8333 & 4 && 0.8776 & 4 && 0.8621 & 5 && 0.5789 & 7 && 365 & 481 & 0.7588 \\
FSM$^{SVM}$ & 0.2292 & 2 && 0.4082 & 4 && 0.5426 & 4 && 0.3500 & 4 && 148 & 388 & 0.3814 \\
GAS-E & 0.3750 & 4 && 0.4694 & 4 && 0.4574 & 4 && 0.4100 & 4 && 166 & 388 & 0.4278 \\

@@

GPRank & 0.8710 & 3 && 0.7253 & 3 && 0.6591 & 3 && 0.8173 & 3 && 290 & 376 & 0.7713 \\

@@

GroupCE & 0.7312 & 3 && - & - && 0.7273 & 3 && 0.7212 & 3 && 207 & 285 & 0.7263 \\
GroupMLE & 0.5269 & 3 && - & - && 0.6250 & 3 && 0.6538 & 3 && 172 & 285 & 0.6035 \\
IntervalRank & 0.5897 & 1 && 0.3750 & 1 && - & - && 0.3158 & 1 && 50 & 117 & 0.4274 \\
IPRank & 0.9355 & 3 && 0.8132 & 3 && 0.7955 & 3 && 0.8514 & 6 && 357 & 420 & 0.8500 \\

@@

LambdaMART & 0.5714 & 2 && - & - && 1.0000 & 1 && 0.6786 & 3 && 54 & 81 & 0.6667 \\

@@

LARF & 0.9892 & 3 && 0.9890 & 3 && 0.9886 & 3 && 0.9808 & 3 && 371 & 376 & 0.9867 \\
Linear Regression & 0.0714 & 9 && 0.1099 & 9 && 0.0829 & 8 && 0.0650 & 8 && 63 & 761 & 0.0828 \\
ListMLE & 0.0000 & 1 && - & - && 0.0213 & 4 && 0.00962 & 3 && 3 & 199 & 0.0151 \\
ListNet & 0.4495 & 12 && 0.4911 & 12 && 0.5982 & 12 && 0.4504 & 12 && 460 & 928 & 0.496 \\
ListReg & 0.7312 & 3 && 0.6923 & 3 && - & - && 0.4327 & 3 && 176 & 288 & 0.6111 \\
LRUF & 0.9823 & 4 && 0.9817 & 4 && 0.9818 & 4 && 0.9680 & 4 && 447 & 457 & 0.9781 \\

@@

NewLoss & 0.5161 & 3 && 0.4286 & 3 && 0.3977 & 3 && - & - && 122 & 272 & 0.4485 \\
OWPC & 0.6500 & 6 && - & - && - & - && 0.6241 & 6 && 166 & 261 & 0.6360 \\
PERF-MAP & 0.3894 & 4 && 0.2661 & 4 && 0.2000 & 4 && 0.7680 & 4 && 191 & 457 & 0.4179 \\

@@

Rank-PMBGP & - & - && 0.7692 & 1 && 0.2727 & 1 && 0.8750 & 1 && 24 & 40 & 0.6750 \\

@@

RankBoost & 0.3211 & 12 && 0.2794 & 10 && 0.3936 & 17 && 0.3134 & 14 && 309 & 939 & 0.3291 \\

@@

RankELM (pairwise) & 0.6154 & 1 && 0.6500 & 1 && 0.6944 & 1 && 0.5143 & 2 && 111 & 185 & 0.6000 \\
RankELM (pointwise) & 0.6923 & 1 && 0.7000 & 1 && 0.8056 & 1 && 0.5429 & 2 && 122 & 185 & 0.6595 \\

@@

RankNet & 0.1887 & 1 && 0.2857 & 3 && 0.5915 & 5 && - & - && 66 & 173 & 0.3815 \\

@@

RankSVM & 0.3010 & 12 && 0.3613 & 11 && 0.4496 & 17 && 0.3400 & 13 && 323 & 885 & 0.3650 \\
RankSVM-Primal & 0.3920 & 8 && 0.4509 & 8 && 0.4591 & 7 && 0.3520 & 7 && 283 & 687 & 0.4119 \\
RankSVM-Struct & 0.3520 & 9 && 0.4136 & 9 && 0.4467 & 9 && 0.3624 & 9 && 315 & 793 & 0.3928 \\

@@

REG-SHG-SDCG & 0.3846 & 1 && 0.4500 & 1 && - & - && 0.6579 & 1 && 58 & 117 & 0.4957 \\
Ridge Regression & 0.4088 & 7 && 0.3333 & 7 && 0.3648 & 7 && 0.2905 & 7 && 226 & 650 & 0.3477 \\
RSRank & 0.5729 & 4 && 0.5306 & 4 && 0.6277 & 4 && 0.6600 & 4 && 232 & 388 & 0.5979 \\

@@

SmoothRank & 0.6038 & 7 && 0.6340 & 7 && 0.6415 & 7 && 0.5307 & 7 && 390 & 650 & 0.6000 \\
SoftRank & 0.2308 & 1 && 0.2750 & 1 && 0.6111 & 1 && - & - && 42 & 115 & 0.3652 \\
SortNet & 0.2500 & 2 && 0.5147 & 4 && 0.5667 & 4 && 0.5000 & 2 && 113 & 238 & 0.4748 \\
SparseRank & 0.8224 & 4 && 0.8173 & 4 && 0.7944 & 4 && - & - && 258 & 318 & 0.8113 \\
SVM$^{MAP}$ & 0.2893 & 7 && 0.3801 & 8 && 0.3591 & 8 && 0.3498 & 10 && 254 & 734 & 0.3460 \\

@@

TGRank & 0.5417 & 4 && 0.6122 & 4 && 0.5000 & 4 && 0.4600 & 4 && 205 & 388 & 0.5284 \\

>>>>

\subsection{Literature Selection}
Table 4 in the appendix gives an overview of the learning to rank methods for which evaluation results were found through the described procedure. Occurrences of L2, L3 and L4 in Table 4 imply that these algorithms are evaluated as official LETOR 2.0, 3.0 and 4.0 baselines respectively.\\

@@

\subsection{Cross-Metric}
\begin{figure}
\centering
\includegraphics[scale=0.21]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_all}
\end{figure}
Figure \ref{fig:normalized_winning_number_all} shows the NWN as function of IWN for the methods described in Table 4. The cross-metric comparison is based on the NDCG@$\{3,5,10\}$ and MAP comparisons combined, which justifies analyzing the comparison more thoroughly. Figure \ref{fig:normalized_winning_number_all} labels the algorithms with no other algorithm having a higher value on both the horizontal axis and vertical axis, but also labels the algorithms with exactly one algorithm having a higher value on both axes with smaller font size. In addition, Linear Regression and the ranking method of simply sorting on the best single feature are labelled as baselines.\\

@@

@@

AdaRank-MAP & 0.3529 & 12 && 0.3884 & 12 && 0.3648 & 13 && 0.3206 & 12 && 334 & 940 & 0.3553 \\
AdaRank-NDCG & 0.3122 & 12 && 0.3259 & 12 && 0.3158 & 16 && 0.2863 & 12 && 295 & 954 & 0.3092 \\

@@

ApproxNDCG & 0.8000 & 1 && 0.7500 & 1 && 0.8611 & 1 && - & - && 93 & 116 & 0.8017 \\
BagBoo & 0.8333 & 2 && 0.8400 & 1 && - & - && 0.6545 & 2 && 97 & 128 & 0.7578 \\

@@

BL-MART & 0.8776 & 3 && 0.7200 & 1 && - & - && 0.8036 & 3 && 106 & 130 & 0.8154 \\
BoltzRank-Pair & 0.8286 & 4 && 0.8350 & 4 && - & - && 0.5804 & 5 && 256 & 351 & 0.7293 \\
BoltzRank-Single & 0.7524 & 4 && 0.7184 & 4 && - & - && 0.4336 & 5 && 215 & 351 & 0.6125 \\

@@

CoList & 1.0000 & 1 && 1.0000 & 1 && 0.1667 & 1 && - & - && 3 & 8 & 0.3750 \\

@@

DCMP & 0.5477 & 9 && 0.5079 & 9 && 0.5888 & 9 && - & - && 322 & 587 & 0.5486 \\

@@

EnergyNDCG & 0.3778 & 2 && 0.3778 & 2 && 0.4146 & 2 && - & - && 51 & 131 & 0.3893 \\
FBPCRank & 0.4235 & 3 && 0.5529 & 3 && - & - && - & - && 83 & 170 & 0.4882 \\
FenchelRank & 0.7760 & 5 && 0.7500 & 5 && 0.7623 & 5 && 0.6418 & 5 && 369 & 505 & 0.7307 \\
FocusedBoost & 0.3753 & 2 && 0.4545 & 2 && 0.6863 & 2 && - & - && 73 & 143 & 0.5105 \\

@@

FocusedSVM & 0.2371 & 2 && 0.2727 & 2 && 0.6078 & 2 && - & - && 55 & 143 & 0.3846 \\

@@

FRank & 0.3137 & 11 && 0.2849 & 10 && 0.3029 & 11 && 0.2623 & 11 && 244 & 842 & 0.2898 \\
FSMRank & 0.8351 & 4 && 0.8776 & 4 && 0.8621 & 5 && 0.5789 & 7 && 366 & 482 & 0.7593 \\
FSM$^{SVM}$ & 0.2292 & 2 && 0.4082 & 4 && 0.5426 & 4 && 0.3500 & 4 && 149 & 389 & 0.3830 \\
GAS-E & 0.3814 & 4 && 0.4694 & 4 && 0.4574 & 4 && 0.4100 & 4 && 167 & 389 & 0.4293 \\

@@

GPRank & 0.8750 & 3 && 0.7253 & 3 && 0.6591 & 3 && 0.8173 & 3 && 293 & 379 & 0.7731 \\

@@

GroupCE & 0.7292 & 3 && - & - && 0.7273 & 3 && 0.7212 & 3 && 209 & 288 & 0.7257 \\
GroupMLE & 0.5208 & 3 && - & - && 0.6250 & 3 && 0.6538 & 3 && 173 & 288 & 0.6007 \\
IntervalRank & 0.6000 & 1 && 0.3750 & 1 && - & - && 0.3158 & 1 && 51 & 118 & 0.4322 \\
IPRank & 0.9375 & 3 && 0.8132 & 3 && 0.7955 & 3 && 0.8514 & 6 && 360 & 423 & 0.8511 \\

@@

LambdaMART & 0.4082 & 3 && - & - && 1.0000 & 1 && 0.6786 & 3 && 62 & 109 & 0.5688 \\

@@

LARF & 0.9896 & 3 && 0.9890 & 3 && 0.9886 & 3 && 0.9808 & 3 && 374 & 379 & 0.9868 \\
Linear Regression & 0.0754 & 9 && 0.1099 & 9 && 0.0829 & 8 && 0.0650 & 8 && 64 & 771 & 0.0830 \\
ListMLE & 0.0000 & 2 && 0.0000 & 1 && 0.0213 & 4 && 0.00962 & 3 && 3 & 240 & 0.0125 \\
ListNet & 0.4480 & 12 && 0.4911 & 12 && 0.5982 & 12 && 0.4504 & 12 && 461 & 931 & 0.4952 \\
ListReg & 0.7292 & 3 && 0.6923 & 3 && - & - && 0.4327 & 3 && 178 & 291 & 0.6117 \\
LRUF & 0.9828 & 4 && 0.9817 & 4 && 0.9818 & 4 && 0.9680 & 4 && 450 & 460 & 0.9783 \\

@@

NewLoss & 0.5208 & 3 && 0.4286 & 3 && 0.3977 & 3 && - & - && 124 & 275 & 0.4509 \\
OWPC & 0.6475 & 6 && - & - && - & - && 0.6241 & 6 && 167 & 263 & 0.6350 \\
PERF-MAP & 0.3966 & 4 && 0.2661 & 4 && 0.2000 & 4 && 0.7680 & 4 && 193 & 460 & 0.4196 \\

@@

Rank-PMBGP & - & - && 0.7692 & 1 && 0.2727 & 1 && 0.8750 & 1 && 27 & 40 & 0.6750 \\

@@

RankBoost & 0.3303 & 12 && 0.2794 & 10 && 0.3936 & 17 && 0.3134 & 14 && 312 & 942 & 0.3312 \\

@@

RankELM (pairwise) & 0.6475 & 1 && 0.6500 & 1 && 0.6944 & 1 && 0.5143 & 2 && 112 & 186 & 0.6022 \\
RankELM (pointwise) & 0.7000 & 1 && 0.7000 & 1 && 0.8056 & 1 && 0.5429 & 2 && 123 & 186 & 0.6613 \\

@@

RankNet & 0.1887 & 3 && 0.2857 & 3 && 0.5915 & 5 && - & - && 66 & 173 & 0.3815 \\

@@

RankSVM & 0.3014 & 12 && 0.3613 & 11 && 0.4496 & 17 && 0.3400 & 13 && 324 & 888 & 0.3649 \\
RankSVM-Primal & 0.3911 & 8 && 0.4509 & 8 && 0.4591 & 7 && 0.3520 & 7 && 284 & 690 & 0.4116 \\
RankSVM-Struct & 0.3518 & 9 && 0.4136 & 9 && 0.4467 & 9 && 0.3624 & 9 && 316 & 805 & 0.3925 \\

@@

REG-SHG-SDCG & 0.4000 & 1 && 0.4500 & 1 && - & - && 0.6579 & 1 && 59 & 118 & 0.5000 \\
Ridge Regression & 0.4074 & 7 && 0.3333 & 7 && 0.3648 & 7 && 0.2905 & 7 && 227 & 653 & 0.3476 \\
RSRank & 0.5773 & 4 && 0.5306 & 4 && 0.6277 & 4 && 0.6600 & 4 && 233 & 389 & 0.5990 \\

@@

SmoothRank & 0.6049 & 7 && 0.6340 & 7 && 0.6415 & 7 && 0.5307 & 7 && 392 & 653 & 0.6003 \\
SoftRank & 0.2500 & 1 && 0.2750 & 1 && 0.6111 & 1 && - & - && 43 & 116 & 0.3707 \\
SortNet & 0.2667 & 2 && 0.5147 & 4 && 0.5667 & 4 && 0.5000 & 2 && 114 & 239 & 0.4770 \\
SparseRank & 0.8241 & 4 && 0.8173 & 4 && 0.7944 & 4 && - & - && 259 & 319 & 0.8119 \\
SVM$^{MAP}$ & 0.2901 & 7 && 0.3801 & 8 && 0.3591 & 8 && 0.3498 & 10 && 255 & 737 & 0.3460 \\

@@

TGRank & 0.5464 & 4 && 0.6122 & 4 && 0.5000 & 4 && 0.4600 & 4 && 206 & 389 & 0.5296 \\
